Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2020-11-06 Supporting_Information.Rmd
Removed reference to equations in the main text

\
Among the `r length(sp.exp.param$sp)` species with observed data on ($K_\textrm{leaf}$ vs. $\mathrm{\Psi}$~leaf~) used to build the community-level models of leaf vulnerability curves (Eqs. \@ref(eq:b-mod)-\@ref(eq:a-mod)), two lacked data on WSG and five on LMA~lamina~. We filled three gaps in LMA using a linear relationship between LMA and LMA~disc~, the latter defined as the mean leaf mass per unit area measured for a 1.483 cm^2^ leaf disc taken to avoid veins (g m^-2^) for leaves receiving direct sunlight ($\overline{\textrm{LMA}} = `r disc.cf[1]` + `r disc.cf[2]`\textrm{LMA}_{disc}$; Adj. $R$^2^ = `r disc.r2`; $p$ `r disc.p`, $n$ = `r disc.n`). We filled the two remaining gaps in LMA using a linear relationship between LMA and LMA~lamina~, as measured during the smaller, $K_\textrm{leaf}$ campaign ($\overline{\textrm{LMA}} = `r lma.cf[1]` + `r lma.cf[2]`\textrm{LMA}_{lamina}$; Adj. $R$^2^ = `r lma.r2`; $p$ `r lma.p`, $n$ = `r lma.n`). We chose not to fill the two data gaps in WSG as available data were poor predictors of WSG.

@@

```{r obs-plc-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-obs-plc-curves}Vulnerability curves fitted to observed $K_\\textrm{leaf}$ vs. $\\mathrm{\\Psi}$~leaf~ data for ", length(sp.exp.param$sp)," tree species from BCI with Eq. \\@ref(eq:vc-exp)--in absolute terms (**a**, **b**), as well as, in terms of loss of conductivity (%) (**c**, **d**). Each line represents a species, color coded by WSG (**a**, **c**), or LMA (**b**, **d**), with blue tones indicating smaller values of WSG or LMA and red tones indicating larger values.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/plot.obs.plc.jpeg"))
```

>>>>

\
Among the `r length(sp.exp.param$sp)` species with observed data on ($K_\textrm{leaf}$ vs. $\mathrm{\Psi}$~leaf~) used to build the community-level models of leaf vulnerability curves, two lacked data on WSG and five on LMA~lamina~. We filled three gaps in LMA using a linear relationship between LMA and LMA~disc~, the latter defined as the mean leaf mass per unit area measured for a 1.483 cm^2^ leaf disc taken to avoid veins (g m^-2^) for leaves receiving direct sunlight ($\overline{\textrm{LMA}} = `r disc.cf[1]` + `r disc.cf[2]`\textrm{LMA}_{disc}$; Adj. $R$^2^ = `r disc.r2`; $p$ `r disc.p`, $n$ = `r disc.n`). We filled the two remaining gaps in LMA using a linear relationship between LMA and LMA~lamina~, as measured during the smaller, $K_\textrm{leaf}$ campaign ($\overline{\textrm{LMA}} = `r lma.cf[1]` + `r lma.cf[2]`\textrm{LMA}_{lamina}$; Adj. $R$^2^ = `r lma.r2`; $p$ `r lma.p`, $n$ = `r lma.n`). We chose not to fill the two data gaps in WSG as available data were poor predictors of WSG.

@@

```{r obs-plc-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-obs-plc-curves}Vulnerability curves fitted to observed $K_\\textrm{leaf}$ vs. $\\mathrm{\\Psi}$~leaf~ data for ", length(sp.exp.param$sp)," tree species from BCI--in absolute terms (**a**, **b**), as well as, in terms of loss of conductivity (%) (**c**, **d**). Each line represents a species, color coded by WSG (**a**, **c**), or LMA (**b**, **d**), with blue tones indicating smaller values of WSG or LMA and red tones indicating larger values.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/plot.obs.plc.jpeg"))
```
